{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-01-31 Paper/main.tex
More fpcr theory

	\begin{equation}
		\tilde{\xi}^{m,L}_{i} = \sum_{j = 1}^{L} \left[ a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s\right]
	\end{equation}

@@

	% maybe use n for coefficents in expansion of nu? before b for beta, so this could be a consistent choice

>>>>

	\begin{equation}\label{score_approx}
		\hat{\xi}_{i}^m \approx \sum_{j = 1}^{L} \left[ a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s\right] =: \tilde{\xi}^{m,L}_{i}
	\end{equation}

@@

	Using the Karhunen-Lo\'{e}ve Expansion to represent $X(\omega)$, it is also possible to express the data generating process in a slightly different way.

	\begin{equation}
		\begin{split}
			Y(\omega) &= \alpha + \int_{0}^{1} {\color{red}X(\omega)(s)} \beta(s) \mathrm{d}s + \epsilon(\omega)
			= \alpha + \int_{0}^{1} {\color{red}\left(\mu(s) + \sum_{m \in \mathcal{M}} \xi^m(\omega) \nu^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon(\omega)\\
			&= {\color{teal}\alpha + \int_{0}^{1} \mu(s) \beta(s) \mathrm{d}s} + \sum_{m \in \mathcal{M}} \xi^m(\omega) {\color{violet}\int_{0}^{1} \nu^m(s) \beta(s) \mathrm{d}s} + \epsilon(\omega)
			= {\color{teal}\bar{\alpha}} + \sum_{m \in \mathcal{M}} \xi^m(\omega) {\color{violet}\beta^m} + \epsilon(\omega)
		\end{split}
	\end{equation}

	As these theoretical Eigenfunctions and Eigenvalues are typically unknown, the corresponding equation in sample analogues is more interesting as a representation of an observation.

	\begin{equation}
		\begin{split}
			y_i &= \alpha + \int_{0}^{1} {\color{red}x_i(s)} \beta(s) \mathrm{d}s + \epsilon_i
			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m \in \mathcal{M}} \hat{\xi}^m_i \hat{\nu}^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon_i\\
			&= {\color{teal}\alpha + \int_{0}^{1} \hat{\mu}(s) \beta(s) \mathrm{d}s} + \sum_{m \in \mathcal{M}} \hat{\xi}^m_i {\color{violet}\int_{0}^{1} \hat{\nu}^m(s) \beta(s) \mathrm{d}s} + \epsilon_i
			= {\color{teal}\bar{\alpha}} + \sum_{m \in \mathcal{M}} \hat{\xi}^m_i {\color{violet}\hat{\beta}^m} + \epsilon_i
		\end{split}
	\end{equation}

	This, however, is a simplification for the purposes of real-world estimation as in most implementations the coefficient function and the principal components are also expressed or derived in terms of a basis that can be chosen freely. Introducing both concepts one step at a time leads to the following complication if we first introduce an expansion of the coefficient function.

	\begin{equation}
		\begin{split}
			y_i &= \alpha + \int_{0}^{1} {\color{red}x_i(s)} {\color{blue}\beta(s)} \mathrm{d}s + \epsilon_i
			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m \in \mathcal{M}} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right)} {\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} \mathrm{d}s + \epsilon_i\\
			&= \alpha + \int_{0}^{1} \left[ \sum_{j \in \mathcal{I}} b_j \phi_j(s) \hat{\mu}(s) + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \hat{\nu}^m(s) \phi_j(s) \right] \right] \mathrm{d}s + \epsilon_i \\
			&= \alpha + \sum_{j \in \mathcal{I}} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
		\end{split}
	\end{equation}

	If we additionally derive and approximate the principal components and corresponding scores using a truncated basis representation as in Equation \ref{score_approx} we obtain the following. To not complicate things more than necessary, the following equation assumes that the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ was used in the derivation of the principal components and the expansion of the coefficient function. Additionally, the following approximation also truncates the basis for the expansion of the coeffieicnt function at the same parameter $L$ that was used for the approximation of the principal components and scores.

	\begin{equation}
		\begin{split}
			y_i & \approx {\color{teal}\alpha + \sum_{j = 1}^{L} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s} +  \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} {\color{blue}\hat{\nu}^{m,L}(s)} \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega) \\
			& \approx {\color{teal} \tilde{\alpha}} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1}{\color{blue}\left(\sum_{k = 1}^{L} n_{k}^m \phi_{k}(s)\right)} \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega) \\
			& \approx \tilde{\alpha} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} {\color{red}\sum_{j = 1}^{L} \left[ b_j \sum_{k = 1}^{L} n_{k}^m \int_{0}^{1} \phi_{k}(s) \phi_j(s) \mathrm{d}s \right]} \right]+ \epsilon(\omega)
			= \tilde{\alpha} + \sum_{m  = 1}^{M} \tilde{\xi}^{m,L}_{i} {\color{red}\tilde{\beta}^{m,L}}+ \epsilon(\omega)
		\end{split}
	\end{equation}
